Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-15 paper.tex
Martin is also a corresponding author
Find example where extrapolating small scale experiments causes errors; resolves #61
Better explain why HAWT research is relevant; closes #46

% Authors (Add full first names)
\Author{Peter Bachant $^{1,}$* and Martin Wosnik $^{1}$}

@@

With regards to wind and marine hydrokinetic (MHK) turbines, scaled physical
models are used to validate predictive numerical models, predict full-scale
performance of individual turbines, and design or investigate arrays of devices.
Scaled models have the benefit of being significantly less expensive, however, a
key question is whether or not an acceptable scale mismatch exists. Similarly,
it is questionable whether numerical models validated with physical model data
obtained orders of magnitude away from prototype scale should be considered
validated at all.

@@

Krogstad and Adaramola \cite{Krogstad2012a} observed Reynolds number
independence of the performance of a 0.9 m diameter axial-flow turbine rotor at
$Re_D \approx 5 \times 10^5$ in wind tunnel tests. Their turbine blades had an
S826 profile along their entire span, a profile chosen for its
$Re$-independence. Walker et al. \cite{Walker2014} similarly chose a NACA 63-618
foil for their axial-flow turbine tests in a towing tank, which were performed
at a mid-span Reynolds number $Re_c = 4 \times 10^5$. McTavish et al.
\cite{McTavish2013} showed how the near-wake expansion for an axial-flow rotor
is increased at higher Reynolds numbers, concluding that physical models should
be designed with $Re$-independence in mind if they are to be run at low $Re$.

>>>>

% Authors (Add full first names)
\Author{Peter Bachant $^{1,}$* and Martin Wosnik $^{1}$*}

@@

With regards to wind and marine hydrokinetic (MHK) turbines, scaled physical
models are used to validate predictive numerical models, predict full-scale
performance of individual turbines, and design or investigate arrays of devices.
Scaled models have the benefit of being significantly less expensive, however, a
key question is whether or not an acceptable scale mismatch exists. Similarly,
it is questionable whether numerical models validated with physical model data
obtained orders of magnitude away from prototype scale should be considered
validated at all. An example of the errors that can result from the
extrapolation of small scale experiments can be found in \cite{Baker1991}.

@@

Scale effects on axial-flow or horizontal-axis wind turbines are better
understood, and investigators have methods for compensating. Krogstad and
Adaramola \cite{Krogstad2012a} observed Reynolds number independence of the
performance of a 0.9 m diameter axial-flow turbine rotor at $Re_D \approx 5
\times 10^5$ in wind tunnel tests. Their turbine blades had an S826 profile
along their entire span, a profile chosen for its $Re$-independence. Walker et
al. \cite{Walker2014} similarly chose a NACA 63-618 foil for their axial-flow
turbine tests in a towing tank, which were performed at a mid-span Reynolds
number $Re_c = 4 \times 10^5$. McTavish et al. \cite{McTavish2013} showed how
the near-wake expansion for an axial-flow rotor is increased at higher Reynolds
numbers, concluding that physical models should be designed with
$Re$-independence in mind if they are to be run at low $Re$. It is uncertain,
however, if these methods work equally well for cross-flow turbines.
